hormones

### 2020-02-03 analysis/07_hormones.Rmd
better figures

printaovtablesex("prolactin", "PRL ~ sex")
```

@@

p1 <- hormones %>%
  filter(hormone == "corticosterone",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "concentration (ng/mL)", subtitle = "Corticosterone" , x = NULL) +
  theme(legend.position = "none") +
  scale_y_continuous(limits = c(0,8.5)) +
  scale_fill_manual(values = sexcolors)
p1

@@

p2 <-  ggplot(cort, aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = NULL, x = NULL, subtitle = " ") +
  theme(legend.position = "none") +
  geom_signif(comparisons=list(c("control", "inc.d17")), annotations= "p = 0.49", y_position = 7.5, tip_length = 0, vjust = 0, color= "black" , textsize = 3 ) +
  geom_signif(comparisons=list(c("control", "hatch")), annotations= "p = 0.021", y_position = 8, tip_length = 0, vjust = 0, color= "black" , textsize = 3 ) +
  geom_signif(comparisons=list(c("control", "n5")), annotations= "p = 0.004", y_position = 8.5, tip_length = 0, vjust = 0, color= "black" , textsize = 3 ) +
  geom_signif(comparisons=list(c("n5", "n9")), annotations= "p = 0.001", y_position = 8, tip_length = 0, vjust = 0, color= "black" , textsize = 3 ) +
  scale_y_continuous(limits = c(0,8.5))

@@

p12 <- plot_grid(p1,p2, rel_widths = c(0.2,0.8), labels = c("a","b"), label_size = 8)

p3 <- hormones %>%
  filter(hormone == "corticosterone",
         treatment %in% c(controlsremoval, levelsremoval )) %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot() +
  theme_B3() +
  scale_y_continuous(limits = c(0,8.5)) +
  scale_fill_manual(values = colorscharmaip) +
  theme(legend.position = "none") +
  labs( x = NULL, y = "concentration (ng/mL")
p3

p4 <- hormones %>%
  filter(hormone == "corticosterone",
         treatment %in% c(controlstiming, levelstiming )) %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot() +
  theme_B3() +
  scale_y_continuous(limits = c(0,8.5)) +
  scale_fill_manual(values = colorscharmaip) +
  theme(legend.position = "none") +
  labs(y = NULL, x = NULL)
p4

p34 <- plot_grid(p3,p4, rel_widths = c(0.6,0.4), labels = c("c","d"), label_size = 8 )
p34

@@

p1 <- hormones %>%
  filter(hormone == "prolactin",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "concentration (ng/mL)", subtitle = "Prolactin" , x = NULL) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = sexcolors) +
  scale_y_continuous(limits = c(0,100)) 
p1

@@

p2a <-  ggplot(PRLf, aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot(aes(color = sex)) +
  theme_B3() +
  labs(y = NULL, x = NULL, subtitle = "females") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = sexcolors) +
  scale_y_continuous(limits = c(0,100)) +
    geom_text(aes(label = "B", x = 1, y = 100, fontface = "plain"), size = 3) +
   geom_text(aes(label = "A", x = 2, y = 100), size = 3) +
geom_text(aes(label = "A", x = 3, y = 100), size = 3) +
geom_text(aes(label = "B", x = 4, y = 100), size = 3) +
  geom_text(aes(label = "C", x = 5, y = 100), size = 3) +
  geom_text(aes(label = "D", x = 6, y = 100), size = 3) +
  geom_text(aes(label = "D", x = 7, y = 100), size = 3) +
  geom_text(aes(label = "D", x = 8, y = 100), size = 3) +
  geom_text(aes(label = "D", x = 9, y = 100), size = 3)

p2b <-  ggplot(PRLm, aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot(aes(color = sex)) +
  theme_B3() +
  labs(y = NULL, x = NULL, subtitle = "males") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = sexcolors) +
  scale_y_continuous(limits = c(0,100)) +
  geom_text(aes(label = "A", x = 1, y = 100, fontface = "plain"), size = 3) +
   geom_text(aes(label = "A", x = 2, y = 100), size = 3) +
geom_text(aes(label = "B", x = 3, y = 100), size = 3) +
geom_text(aes(label = "B", x = 4, y = 100), size = 3) +
  geom_text(aes(label = "B", x = 5, y = 100), size = 3) +
  geom_text(aes(label = "D", x = 6, y = 100), size = 3) +
  geom_text(aes(label = "D", x = 7, y = 100), size = 3) +
  geom_text(aes(label = "D", x = 8, y = 100), size = 3) +
  geom_text(aes(label = "D", x = 9, y = 100), size = 3)

@@

p3a <- hormones %>%
  filter(hormone == "prolactin",
         sex == "female", 
         treatment %in% c(controlsremoval, levelsremoval )) %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot(aes(color = sex)) +
  theme_B3() +
  scale_y_continuous(limits = c(0,100)) +
  scale_fill_manual(values = colorscharmaip) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs( x = NULL, y = "concentration (ng/mL", subtitle = "females") +
  scale_color_manual(values = sexcolors)
p3a

@@

plot_grid(allprolactinplots, allcortplots, nrow = 2)
```

## prolactin 2

```{r PRL2}
hormones %>%
  filter(hormone == "prolactin") %>%
  group_by(sex) %>%
  summarise(m = mean(plasma_conc),
            median = median(plasma_conc))

p1 <- hormones %>%
  filter(hormone == "prolactin",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "concentration (ng/mL)", subtitle = "Prolactin" , x = NULL) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = sexcolors) +
  scale_y_continuous(limits = c(0,100)) 
p1

df <- hormones %>%
  filter(hormone == "prolactin",
         study == "characterization")
p2 <-  ggplot(df, aes(x = treatment, y = plasma_conc, fill = treatment, color = sex)) +
  geom_boxplot(aes(color = sex)) +
  theme_B3() +
  labs(y = NULL, x = NULL, subtitle = " ") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = sexcolors) +
  scale_y_continuous(limits = c(0,105)) +
    geom_text(aes(label = "B", x = 1, y = 100, fontface = "plain"), size = 3) +
   geom_text(aes(label = "A", x = 2, y = 100), size = 3) +
geom_text(aes(label = "A", x = 3, y = 100), size = 3) +
geom_text(aes(label = "B", x = 4, y = 100), size = 3) +
  geom_text(aes(label = "C", x = 5, y = 100), size = 3) +
  geom_text(aes(label = "D", x = 6, y = 100), size = 3) +
  geom_text(aes(label = "D", x = 7, y = 100), size = 3) +
  geom_text(aes(label = "D", x = 8, y = 100), size = 3) +
  geom_text(aes(label = "D", x = 9, y = 100), size = 3) +
  geom_text(aes(label = '*', x = 1, y = 105), size = 5) +
   geom_text(aes(label = '*', x = 2, y = 105), size = 5) 
  p2

p3 <- hormones %>%
  filter(hormone == "prolactin",
         treatment %in% c(controlsremoval, levelsremoval )) %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot(aes(color = sex)) +
  theme_B3() +
  scale_y_continuous(limits = c(0,110)) +
  scale_fill_manual(values = colorscharmaip) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs( x = NULL, y = "concentration (ng/mL", subtitle = " ") +
  scale_color_manual(values = sexcolors) +
   geom_text(aes(label = '*', x = 2, y = 105), size = 5) 
p3

p4 <- hormones %>%
  filter(hormone == "prolactin",
         treatment %in% c(controlstiming, levelstiming )) %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot(aes(color = sex)) +
  theme_B3() +
  scale_y_continuous(limits = c(0,110)) +
  scale_fill_manual(values = colorscharmaip) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = NULL, x = NULL, subtitle = " ") +
  scale_color_manual(values = sexcolors) 
p4

p12 <- plot_grid(p1, p2, rel_widths = c(0.15,0.8), labels = "auto", label_size = 8)
p34 <- plot_grid(p3,p4, nrow = 1, rel_widths = c(0.55,0.45), labels = c("c", "d"), label_size = 8)

plot_grid(p12, p34, nrow = 2)
```

@@

p1 <- hormones %>%
  filter(hormone == "progesterone",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "concentration (ng/mL)", subtitle = "Progesterone" , x = NULL) +
  theme(legend.position = "none")   +
  scale_y_continuous(limits = c(0,4.5)) +
  scale_fill_manual(values = sexcolors)

@@

p3 <- hormones %>%
  filter(hormone == "progesterone",
         treatment %in% c(controlsremoval, levelsremoval )) %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot() +
  theme_B3() +
  scale_y_continuous(limits = c(0,4.5)) +
  scale_fill_manual(values = colorscharmaip) +
  theme(legend.position = "none") +
  labs( x = NULL, y = "concentration (ng/mL")

@@

p5 <- hormones %>%
  filter(hormone == "estradiol",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "concentration (ng/mL)", subtitle = "Estradiol" , x = NULL) +
  theme(legend.position = "none")  +
    scale_y_continuous(limits = c(0,1)) +
  scale_fill_manual(values = sexcolors)

@@

p7 <- hormones %>%
  filter(hormone == "estradiol",
         treatment %in% c(controlsremoval, levelsremoval )) %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot() +
  theme_B3() +
  scale_y_continuous(limits = c(0,1)) +
  scale_fill_manual(values = colorscharmaip) +
  theme(legend.position = "none") +
  labs( x = NULL, y = "concentration (ng/mL")

@@

p9 <- hormones %>%
  filter(hormone == "testosterone",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "concentration (ng/mL)", subtitle = "Testosterone" , x = NULL) +
  theme(legend.position = "none")  +
    scale_y_continuous(limits = c(0,8.5)) +
  scale_fill_manual(values = sexcolors)

@@

```{r supplefig, fig.height=8}
sexsteroids <- plot_grid(p1, p2, p3 + labs(y = NULL), p4, p5, p6, p7 + labs(y = NULL), p8, 
          p9, p10, p11 + labs(y = NULL), p12, nrow = 3, rel_widths =   c(0.175,0.4,0.35,0.25), align = "hv",
          label_size = 8, labels = c("a", " ", " " , " ",
                                     "b", " ", " " , " ",
                                     "c", " ", " " , " "))
sexsteroids
```

>>>>

table1 <- printaovtablesex("prolactin", "PRL ~ sex")
table1
write.csv(table1, "../../parentalhormones/data/table-1.csv", row.names = F)
```

@@

p1 <- hormones %>%
  filter(hormone == "corticosterone",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "CORT (ng/mL)", subtitle = element_blank() , x = NULL) +
  theme(legend.position = "none") +
  scale_fill_manual(values = sexcolors)
p1

@@

p2 <-  ggplot(cort, aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = NULL, x = NULL, subtitle = element_blank() ) +
  theme(legend.position = "none")

@@

p12 <- plot_grid(p1,p2, rel_widths = c(0.2,0.8), labels = c("h","i"), label_size = 8)

p3 <- hormones %>%
  filter(hormone == "corticosterone",
         treatment %in% c(controlsremoval, levelsremoval )) %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot() +
  theme_B3() +
  scale_fill_manual(values = colorscharmaip) +
  theme(legend.position = "none") +
  labs( x = NULL, y = "CORT (ng/mL") +
  ylim(c(0,12.5))
p3

p4 <- hormones %>%
  filter(hormone == "corticosterone",
         treatment %in% c(controlstiming, levelstiming )) %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot() +
  theme_B3() +
  scale_fill_manual(values = colorscharmaip) +
  theme(legend.position = "none") +
  labs(y = NULL, x = NULL) + 
  ylim(c(0,12.5))
p4

p34 <- plot_grid(p3,p4, rel_widths = c(0.6,0.4), labels = c("j","k"), label_size = 8 )
p34

@@

p1 <- hormones %>%
  filter(hormone == "prolactin",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "Prolactin (ng/mL)", subtitle = " " , x = NULL) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = sexcolors) +
  scale_y_continuous(limits = c(0,100)) 
p1

@@

p2a <-  ggplot(PRLf, aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot(aes(color = sex)) +
  theme_B3() +
  labs(y = NULL, x = NULL, subtitle = "females") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = sexcolors) +
  scale_y_continuous(limits = c(0,100))

p2b <-  ggplot(PRLm, aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot(aes(color = sex)) +
  theme_B3() +
  labs(y = NULL, x = NULL, subtitle = "males") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = sexcolors) +
  scale_y_continuous(limits = c(0,100))

@@

p3a <- hormones %>%
  filter(hormone == "prolactin",
         sex == "female", 
         treatment %in% c(controlsremoval, levelsremoval )) %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot(aes(color = sex)) +
  theme_B3() +
  scale_y_continuous(limits = c(0,100)) +
  scale_fill_manual(values = colorscharmaip) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs( x = NULL, y = "Prolactin (ng/mL", subtitle = "females") +
  scale_color_manual(values = sexcolors)
p3a

@@

plot_grid(allprolactinplots, allcortplots, nrow = 2)

@@

p1 <- hormones %>%
  filter(hormone == "progesterone",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "Progesterone (ng/mL)", subtitle = element_blank() , x = NULL) +
  theme(legend.position = "none")   +
  scale_y_continuous(limits = c(0,4.5)) +
  scale_fill_manual(values = sexcolors)

@@

p3 <- hormones %>%
  filter(hormone == "progesterone",
         treatment %in% c(controlsremoval, levelsremoval )) %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot() +
  theme_B3() +
  scale_y_continuous(limits = c(0,4.5)) +
  scale_fill_manual(values = colorscharmaip) +
  theme(legend.position = "none") +
  labs( x = NULL, y = "Progesterone (ng/mL")

@@

p5 <- hormones %>%
  filter(hormone == "estradiol",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "Estradiol (ng/mL)", subtitle = element_blank() , x = NULL) +
  theme(legend.position = "none")  +
    scale_y_continuous(limits = c(0,1)) +
  scale_fill_manual(values = sexcolors)

@@

p7 <- hormones %>%
  filter(hormone == "estradiol",
         treatment %in% c(controlsremoval, levelsremoval )) %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
  geom_boxplot() +
  theme_B3() +
  scale_y_continuous(limits = c(0,1)) +
  scale_fill_manual(values = colorscharmaip) +
  theme(legend.position = "none") +
  labs( x = NULL, y = "Estradiol (ng/mL")

@@

p9 <- hormones %>%
  filter(hormone == "testosterone",
         study == "characterization") %>%
  ggplot(aes(x = sex, y = plasma_conc, fill = sex)) +
  geom_boxplot() +
  theme_B3() +
  labs(y = "Testosterone (ng/mL)", subtitle = element_blank() , x = NULL) +
  theme(legend.position = "none")  +
    scale_y_continuous(limits = c(0,8.5)) +
  scale_fill_manual(values = sexcolors)

@@

```{r sexsteroids2, fig.height=8}
sexsteroids <- plot_grid(
       p9 + theme(axis.text.x = element_blank()),  
       p10 + theme(axis.text.x = element_blank()), 
       p11 + labs(y = NULL) + theme(axis.text.x = element_blank()), 
       p12 + theme(axis.text.x = element_blank()),
        p5 + theme(axis.text.x = element_blank()), 
       p6 + theme(axis.text.x = element_blank()), 
       p7 + labs(y = NULL) + theme(axis.text.x = element_blank()), 
       p8 + theme(axis.text.x = element_blank()), 
       p1 , 
       p2 + theme(axis.text.x = element_text(angle = 45, hjust = 1)), 
       p3 + labs(y = NULL)  + theme(axis.text.x = element_text(angle = 45, hjust = 1)), 
       p4  + theme(axis.text.x = element_text(angle = 45, hjust = 1)), 
        nrow = 3, 
        rel_widths =   c(0.175,0.4,0.35,0.25), align = "hv",
          label_size = 8, labels = c("A1", "A2", "A3" , "A4",
                                     "B1", "B2", "B3" , "B4",
                                     "C1", "C2", "C3" , "C3"))
sexsteroids
